---
title             : "Dominating Lab 8"
shorttitle        : "Domination"

author: 
  - name          : "Jenn Lewis"
    affiliation   : 
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Yoel Everett"
    affiliation   : 
  - name          : "Jackie O'Brien"
    affiliation   : 

affiliation:
  - id            : 
    institution   : "School of R"
    

abstract: |
  We will rock this lab and show that we are master's of R.  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "Rockstars, Science Rules"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---
#Setup packages to be used
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 6.5, fig.height = 8)

library("papaja")
library(ggplot2)
library(tidyverse)
library(rio)
library(here)
```
#load data
```{r load data}
star <- import(here("data", "star.csv" ),
            setclass = "tbl_df")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion
As we found in our meta-analysis (@my_meta) there is a small, but enduring association between parenting styles and child cortisol. One of our co-authors is also a total badass whose paper won an award for best publication (@jenn).


#Commit 4: Table
Boys from non-low income families have an average math score of 492.85 (46.34) and an average reading score of 441.46 (32.32). Boys from low income families have lower average scores in math and reading, 469.87 (46.09) and 425.38 (26.63), respectively. Girls results follow a similar pattern, such that compared to girls from low-income families, girls from non-low income families have higher scores in math, 501.21 (45.96) vs. 477.51 (46.31) and reading, 448.54 (34.52) vs. 430.80 (27.42).

```{r}
library(kableExtra)
table <- star %>%
  group_by(sex, frl) %>%
  summarize(math_mean=mean(tmathss), math_sd=sd(tmathss), rdg_mean=mean(treadss), rdg_sd=sd(treadss))
kable(table, 
      format = "latex", 
      booktabs = TRUE)
```

#Commit 5: Plot

```{r plot, echo = FALSE}

plot<- ggplot(star, aes(totexp, tmathss)) + 
  geom_point(color = "light grey") +
  geom_smooth (aes(color = frl), method = "lm") +
  labs(x = "Teacher Experience (years)", 
     y = "Total Math Scale Score",
     title = "Relation between teacher experience and math scores",
     subtitle = "Separate regression lines displayed by free/reduced price lunch status") +
  theme_minimal()

plot(plot)
```

It appears that there is a main effect of lunch status, such that those who receive paid means exhibit higher total math scores than those who receive free/reduced price meals. There is also a main effect of teacher experience, such that as teacher experience increases, total math scores for students increases, regardless of lunch status. There is no interaction. 




