---
title             : "Dominating Lab 8"
shorttitle        : "Domination"

author: 
  - name          : "Jenn Lewis"
    affiliation   : 
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Yoel Everett"
    affiliation   : 
  - name          : "Jackie O'Brien"
    affiliation   : 

affiliation:
  - id            : 
    institution   : "School of R"
    

abstract: |
  We will rock this lab and show that we are master's of R.  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "Rockstars, Science Rules"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---
#Setup packages to be used
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 6.5, fig.height = 8)

library("papaja")
library(ggplot2)
library(tidyverse)
library(rio)
library(here)
```
#load data
```{r load data}
star <- import(here("data", "star.csv" ),
            setclass = "tbl_df")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup


#Commit 5: Plot

```{r plot, echo = FALSE}

plot<- ggplot(star, aes(totexp, tmathss)) + 
  geom_point(color = "light grey") +
  geom_smooth (aes(color = frl), method = "lm") +
  labs(x = "Teacher Experience (years)", 
     y = "Total Math Scale Score",
     title = "Relation between teacher experience and math scores",
     subtitle = "Separate regression lines displayed by free/reduced price lunch status") +
  theme_minimal()

plot(plot)
```

It appears that there is a main effect of lunch status, such that those who receive paid means exhibit higher total math scores than those who receive free/reduced price meals. There is also a main effect of teacher experience, such that as teacher experience increases, total math scores for students increases, regardless of lunch status. There is no interaction. 




